\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{microtype} 
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Aggressively tuned margins to force a single page
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-0.7in} % Pulled up higher
\addtolength{\textheight}{1.4in} % Expanded bottom boundary

\urlstyle{same}
\textfloatsep 5pt
\raggedbottom
\setlength{\tabcolsep}{0in}

% Tightened section divider padding
\titleformat{\section}{
  \vspace{-5pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\HNLines\vspace{-5pt}]

\newcommand{\HNLines}{\hrule height 0.5pt}

\pdfgentounicode=1

% Tightened list item padding
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeProjectHeading}[3]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #3 \\
      \textit{\small#2} & \\
    \end{tabular*}\vspace{-6pt}
}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
% Squeezed item separations to pull the bottom text up
\newcommand{\resumeItemListStart}{\begin{itemize}[itemsep=0pt, parseitemsep=0pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-6pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%

\begin{document}

%----------HEADER (Elite Pure Typographic Standard)----------
\begin{center}
    {\Huge \scshape Datti Eswara Vara Prasad} \\ \vspace{6pt}
    \small 
    \href{2024ucs0088@iitjammu.ac.in}{2024ucs0088@iitjammu.ac.in} ~\textbar~ 
    +91 70325 88339 ~\textbar~ 
    \href{https://www.linkedin.com/in/datti-eswaravaraprasad-4798a3332}{\textbf{LinkedIn}} ~\textbar~ 
    \href{https://github.com/Eswar2025}{\textbf{GitHub}} ~\textbar~
    \href{https://leetcode.com/u/Eswar_777/}{\textbf{LeetCode}} 
\end{center}


%-----------EDUCATION-----------
\section*{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Indian Institute of Technology (IIT) Jammu}{Jammu, India}
      {Bachelor of Technology in Computer Science and Engineering}{July 2024 -- May 2028}
      \begin{itemize}[leftmargin=0.15in, label={$\bullet$}, itemsep=1pt, parseitemsep=1pt]
        \item \small{\textbf{Cumulative GPA:} 7.30 / 10.00}
        \item \small{\textbf{JEE National Exams:} Ranked in the \textbf{Top 0.6\%} (99.4+ Percentile) out of \textbf{1.5M+ applicants} nationwide.}
        \item \small{\textbf{AlgoUniversity:} Ranked in the \textbf{Top 8\%} nationwide during the algorithmic screening process to qualify for Round 2.}
      \end{itemize}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section*{Projects}
    \resumeSubHeadingListStart

    \resumeProjectHeading
          {Study Sync -- Collaborative Productivity Platform}
          {Next.js 14, TypeScript, Supabase, Zustand, Tailwind CSS}
          {\href{https://study-sync-ydk.vercel.app/}{\textbf{Live}}}
          \resumeItemListStart
            \resumeItem{Engineered a fault-tolerant session state machine with \textbf{TypeScript} and Zustand, utilizing the \textbf{\texttt{navigator.sendBeacon}} API for telemetry to ensure zero data loss during sudden browser terminations.}
            \resumeItem{Architected a scalable, event-driven collaboration dashboard via \textbf{Supabase Realtime}. Implemented a pub/sub architecture to eliminate HTTP polling, enabling near-zero latency data synchronization for \textbf{40+ active users}.}
            \resumeItem{Deployed a highly available Next.js application backed by PostgreSQL, enforcing strict \textbf{Row-Level Security (RLS)} policies at the database level to guarantee enterprise-grade data integrity.}
          \resumeItemListEnd

    \resumeProjectHeading
          {CP Hub -- High-Throughput Developer Metrics API}
          {Node.js, Express, Redis, Render, Vercel, REST APIs}
          {\href{https://high-throughput-cp-page.vercel.app/}{\textbf{Live}}}
          \resumeItemListStart
            \resumeItem{Engineered a high-throughput Node.js REST API to aggregate live Codeforces metrics, utilizing \textbf{\texttt{Promise.allSettled}} for concurrent, fault-tolerant data fetching.}
            \resumeItem{Architected a multi-layer caching system with \textbf{Redis} and in-memory fallbacks. Implemented TTL policies and \textbf{stale-cache recovery} to ensure high availability during upstream API failures.}
            \resumeItem{Optimized the data delivery pipeline to achieve \textbf{sub-2ms cache-hit latency} and successfully load-tested the endpoints at \textbf{600+ requests/sec} using Autocannon to validate backend scalability.}
          \resumeItemListEnd

    \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section*{Technical Skills \& Coursework}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: C++, C, JavaScript (ES6+), TypeScript} \\
     \textbf{Backend \& Frameworks}{: Node.js, Express.js, REST APIs, WebSockets (Socket.io), Next.js 14, React 18} \\
     \textbf{Databases \& Caching}{: PostgreSQL, MongoDB, Redis, Supabase} \\
     \textbf{Tools \& Platforms}{: Git, GitHub, Vercel, Render, Tailwind CSS, Zustand} \\
     \textbf{Relevant Coursework}{: Data Structures, Design and Analysis of Algorithms, Principles of Programming Languages, Object-Oriented Programming}
    }}
 \end{itemize}

%-----------CODING PROFILES-----------
\section*{Coding Profiles}

  \resumeItemListStart
  \resumeItem{\textbf{Problem Solving:} Solved \textbf{600+ algorithmic challenges} across LeetCode, Codeforces, and CodeChef.}
  \resumeItem{\textbf{LeetCode (Max Rating: 1610):} Consistently compete in live Weekly Contests, engineering optimized and bug-free solutions under strict 90-minute time constraints.}
  \resumeItem{\textbf{Codeforces (Max Rating: 1235, Pupil):} Compete in timed algorithmic rounds, writing highly efficient C++ code to solve complex math and data structure problems under standard memory constraints.}
\resumeItemListEnd

%-----------LEADERSHIP & EXTRACURRICULARS-----------
\section*{Leadership \& Extracurriculars}
  \resumeItemListStart
    \resumeItem{\textbf{Head of Media \& PR} | \textit{Anhad'26 \& Pragyan'26 Festivals}: Managed complete media operations by coordinating a volunteer team, providing guidance in photography and videography, and designing 3x6 physical standees via Canva for the campus documentary screening.}
    \resumeItem{\textbf{Media Head} | \textit{IIT Jammu Tinkering Lab \& EBSB Council}: Directed digital media strategy and promotional outreach for the campus innovation hub (2025--2026).}
    \resumeItem{\textbf{NCC Cadet} | \textit{National Cadet Corps}: Successfully completed the rigorous Annual Training Camp (ATC'25), demonstrating strong discipline, teamwork, and adaptability.}
  \resumeItemListEnd

\end{document}